---
title: "Difference-in-Differences and OLS Regressions"
author: Sid Satya
output: 
  pdf_document: 
    keep_tex: true
header-includes:
  - \usepackage{dcolumn}

---

This is a notebook that runs the regressions for my honors thesis project.

```{r libraries, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
# library(ggplot2)
# library(dplyr)
library(stargazer)
library(plm)
library(regclass)
```

## Difference-in-Differences Regressions

Importing Relevant DiD Datasets: 
```{r did_data}
# Wage Datasets
pa_wage <-read.csv(file = "/Users/sidsatya/Desktop/berkeley/senior_year/thesis/aithesis/data/physicians_aides_wage_single.csv",header =  TRUE)
sa_wage <-read.csv(file = "/Users/sidsatya/Desktop/berkeley/senior_year/thesis/aithesis/data/secretary_aides_wage_single.csv",header =  TRUE)

# Employment Datasets
pa_emp <-read.csv(file = "/Users/sidsatya/Desktop/berkeley/senior_year/thesis/aithesis/data/physicians_aides_emp_single.csv",header =  TRUE)
sa_emp <-read.csv(file = "/Users/sidsatya/Desktop/berkeley/senior_year/thesis/aithesis/data/secretary_aides_emp_single.csv",header =  TRUE)
```


### Physicians DiD Regressions: 
```{r did_physicians}
# Wage DiD for Physicians vs. Aides, reg1 = without controls and with FE, reg2 = with controls and with FE 
pa_wage_did_reg1 <- lm(LOGWAGE ~ AI + AIPost + factor(YEAR) + factor(IND1990), data = pa_wage)
pa_wage_did_reg2 <- lm(LOGWAGE ~ AI + AIPost + FRACCOLLEGE + FRACWHITE + FRACFEMALE + AGE + factor(YEAR) + factor(IND1990), data = pa_wage) 

# Employment DiD for Secretaries vs. Aides
pa_emp_did_reg1 <- lm(LOGEMP ~ AI + AIPost + factor(YEAR) + factor(IND1990), data = pa_emp)
pa_emp_did_reg2 <- lm(LOGEMP ~ AI + AIPost + FRACCOLLEGE + FRACWHITE + FRACFEMALE + AGE + factor(YEAR) + factor(IND1990), data = pa_emp)
```

```{r stargazer_did_physicians, echo = TRUE, message=FALSE, warning=FALSE, results='asis'}
stargazer(pa_wage_did_reg1, 
          pa_wage_did_reg2, 
          pa_emp_did_reg1, 
          pa_emp_did_reg2,
          header = FALSE, 
          type = "latex",
          title = "Difference-in-Differences: Physicians and Surgeons as Treatment Group, Nursing, Psychiatric, and Home Health Aides as Control Group",
          omit = c("IND1990", "YEAR"),
          column.labels =c("No Controls", "With Controls", "No Controls", "With Controls"),
          covariate.labels = c("AI", "AI x Post", "Frac. College", "Frac. White", "Frac. Female", "Age"),
          dep.var.labels = c("log(wage)", "log(employment)"),
          omit.stat =c("LL", "ser", "f"), 
          add.lines = list(c("Industry FE?", "Yes", "Yes", "Yes", "Yes"), 
                           c("Year FE?", "Yes", "Yes", "Yes", "Yes"))
          )
```

### Secretaries & Administrative Assistants DiD Regressions

Secretaries DiD Regressions: 

```{r did_secretaries}
# Wage DiD for Secretaries vs. Aides, reg1 = without controls and with FE, reg2 = with controls and with FE 
sa_wage_did_reg1 <- lm(LOGWAGE ~ AI + AIPost + factor(YEAR) + factor(IND1990), data = sa_wage)
sa_wage_did_reg2 <- lm(LOGWAGE ~ AI + AIPost + FRACCOLLEGE + FRACWHITE + FRACFEMALE + AGE + factor(YEAR) + factor(IND1990), data = sa_wage) 

# Employment DiD for Secretaries vs. Aides
sa_emp_did_reg1 <- lm(LOGEMP ~ AI + AIPost + factor(YEAR) + factor(IND1990), data = sa_emp)
sa_emp_did_reg2 <- lm(LOGEMP ~ AI + AIPost + FRACCOLLEGE + FRACWHITE + FRACFEMALE + AGE + factor(YEAR) + factor(IND1990), data = sa_emp)
```

```{r stargazer_did_secretaries, echo = TRUE, message=FALSE, warning=FALSE, results='asis'}
stargazer(sa_wage_did_reg1, 
          sa_wage_did_reg2, 
          sa_emp_did_reg1, 
          sa_emp_did_reg2,
          header = FALSE, 
          type = "latex",
          title = "Difference-in-Differences: Secretaries and Administrative Assistants as Treatment Group, Nursing, Psychiatric, and Home Health Aides as Control Group",
          omit = c("IND1990", "YEAR"),
          column.labels =c("No Controls", "With Controls", "No Controls", "With Controls"),
          covariate.labels = c("AI", "AI x Post", "Frac. College", "Frac. White", "Frac. Female", "Age"),
          dep.var.labels = c("log(wage)", "log(employment)"),
          omit.stat =c("LL", "ser", "f"), 
          add.lines = list(c("Industry FE?", "Yes", "Yes", "Yes", "Yes"), 
                           c("Year FE?", "Yes", "Yes", "Yes", "Yes"))
          )
```


## OLS Regressions 
Importing relevant OLS datasets: 
```{r wage_data}
p_wage_ols <-read.csv(file = "/Users/sidsatya/Desktop/berkeley/senior_year/thesis/aithesis/data/p_wage_ols.csv",header =  TRUE)
s_wage_ols <-read.csv(file = "/Users/sidsatya/Desktop/berkeley/senior_year/thesis/aithesis/data/s_wage_ols.csv",header =  TRUE)
a_wage_ols <-read.csv(file = "/Users/sidsatya/Desktop/berkeley/senior_year/thesis/aithesis/data/a_wage_ols.csv",header =  TRUE)

p_emp_ols <-read.csv(file = "/Users/sidsatya/Desktop/berkeley/senior_year/thesis/aithesis/data/p_emp_ols.csv",header =  TRUE)
s_emp_ols <-read.csv(file = "/Users/sidsatya/Desktop/berkeley/senior_year/thesis/aithesis/data/s_emp_ols.csv",header =  TRUE)
a_emp_ols <-read.csv(file = "/Users/sidsatya/Desktop/berkeley/senior_year/thesis/aithesis/data/a_emp_ols.csv",header =  TRUE)
```


### Wage OLS Regressions: 

```{r wage_ols}
# reg1: without controls, reg2: with controls 
pwagereg1 <- lm(LOGWAGE ~ num_patents, data=p_wage_ols)
pwagereg2 <- lm(LOGWAGE ~ num_patents + FRACCOLLEGE + FRACWHITE + FRACFEMALE + AGE + factor(IND1990), data=p_wage_ols)

swagereg1 <- lm(LOGWAGE ~ num_patents, data=s_wage_ols)
swagereg2 <- lm(LOGWAGE ~ num_patents + FRACCOLLEGE + FRACWHITE + FRACFEMALE + AGE + factor(IND1990), data=s_wage_ols)

awagereg1 <- lm(LOGWAGE ~ num_patents, data=a_wage_ols)
awagereg2 <- lm(LOGWAGE ~ num_patents + FRACCOLLEGE + FRACWHITE + FRACFEMALE + AGE + factor(IND1990), data=a_wage_ols)
```

```{r wage_ols_stargazer, echo = TRUE, message=FALSE, warning=FALSE, results='asis'}
stargazer(pwagereg2, 
          swagereg2, 
          awagereg2,
          header = FALSE, 
          type = "latex", 
          title = "Wage OLS for Each Occupation Against Number of AI-Related Patents by Year",
          omit = c("IND1990"),
          dep.var.caption = "Dependent variable: log(wage)",
          dep.var.labels = "",
          column.labels = c('\\shortstack{Physicians and \\\\ Surgeons}', 
                            '\\shortstack{Secretaries and \\\\ Administrative Assistants}', 
                            '\\shortstack{Nursing, Psychiatric, and \\\\ Home Health Aides}'),
          covariate.labels = c("Num. Patents", "Frac. College", "Frac. White", "Frac. Female", "Age"),
          omit.stat = c("LL", "ser", "f"), 
          add.lines = list(c("Industry Fixed Effects?", "  Yes", "  Yes", "  Yes"))
          )
```

### Employment OLS Regressions: 

```{r emp_ols}
# reg1: without controls, reg2: with controls 
pempreg1 <- lm(LOGEMP ~ num_patents, data=p_emp_ols)
pempreg2 <- lm(LOGEMP ~ num_patents + FRACCOLLEGE + FRACWHITE + FRACFEMALE + AGE + factor(IND1990), data=p_emp_ols)

sempreg1 <- lm(LOGEMP ~ num_patents, data=s_emp_ols)
sempreg2 <- lm(LOGEMP ~ num_patents + FRACCOLLEGE + FRACWHITE + FRACFEMALE + AGE + factor(IND1990), data=s_emp_ols)

aempreg1 <- lm(LOGEMP ~ num_patents, data=a_emp_ols)
aempreg2 <- lm(LOGEMP ~ num_patents + FRACCOLLEGE + FRACWHITE + FRACFEMALE + AGE + factor(IND1990), data=a_emp_ols)
```

```{r emp_ols_stargazer, echo = TRUE, message=FALSE, warning=FALSE, results='asis'}
stargazer(pempreg2, 
          sempreg2, 
          aempreg2,
          header = FALSE, 
          type = "latex", 
          title = "Employment OLS for Each Occupation Against Number of AI-Related Patents by Year",
          omit = c("IND1990"),
          dep.var.caption = "Dependent variable: log(employment)",
          dep.var.labels = "",
          column.labels = c('\\shortstack{Physicians and \\\\ Surgeons}', 
                            '\\shortstack{Secretaries and \\\\ Administrative Assistants}', 
                            '\\shortstack{Nursing, Psychiatric, and \\\\ Home Health Aides}'),
          covariate.labels = c("Num. Patents", "Frac. College", "Frac. White", "Frac. Female", "Age"),
          omit.stat = c("LL", "ser", "f"), 
          add.lines = list(c("Industry Fixed Effects?", "  Yes", "  Yes", "  Yes"))
          )
```